## README


#### Introduction

Hi there! My name is Sam. This is my first time producing a blog. Fortunately I 
have Luis (the other contributor of this blog) takes me under his wings. =) I am
a mathematician believing in that math is for everyone. So here I'm, sharing 
with you my thoughts on the general solutions to some problems posted on 
[Project Euler.net](https://projecteuler.net). Besides the explanations to the 
problems, I will also include the scripts in a programming language called 
[R](http://www.r-project.org/) for the pertinent computations.



#### Why [R](http://www.r-project.org/index.html)?

1. Why not? While languages like Java, C++ and Python are very popular and much 
more familiar to many, it is always great to explore and expand. 

2. R is a high-level language that is designed for (particularly statistical) 
computations. Thus, it has numerous built-in functions which we would have to 
write ourselves or at least import from some libraries if we use other languages.

3. [\$ \$ \$](http://economictimes.indiatimes.com/magazines/panache/these-are-the-highest-paying-programming-languages-you-should-learn-ranked-by-salary/articleshow/45258811.cms)



#### How to Run?

The codes are embedded in the markdown file. To run the scripts, copy and paste 
the codes in the boxes like this one

```{r, results='hide'}
x <- 1
y <- 2
z <- x+y
```

on a new R scipt file, save it as FileNameOfYourChoice.R and then compile. Note 
that sometimes there are boxes with value(s) preceeded by *two* sharp signs as 
shown in the second snippet below,

```{r}
z # Calls for the value of z.
```

These are the results of some evaluations which I use for demonstration and need 
not be copied to run the script.



#### Contact
Please feel free to comment. I would love to hear your thoughts. Enjoy!



